---
title: "VR Analysis PDT/PTT"
author: "JR"
date: "31.05.23 "
output:
  html_document: default
  pdf_document: default
---
load packages
```{r echo=TRUE, message=FALSE, warning=FALSE}
  library(Rmisc) 
  library(readxl)
  library(ggpubr) 
  library(rstatix) 
  library(WRS2)
  library(dplyr) 
  library(effectsize)
```

Load data
```{r}
long_d <- readRDS("long_d_0.rds")
```

Prepare data for pdt analysis
```{r}
aov_pdt<- long_d %>% dplyr::mutate(dom_pdt = t01_pdt0) 
aov_pdt <- droplevels(aov_pdt)
aov_pdt <- aov_pdt %>% dplyr::select(id,gruppe,condition,dom_pdt)
```

Get descriptive statistics grouped by group and condition
("gruppe" = "group" in German) 
```{r}
mean_dom_pdt_gruppe <- aov_pdt %>%
  dplyr::group_by(gruppe) %>%
  dplyr::summarise(mean_pdt = mean(dom_pdt),
            median_dom_pdt = median(dom_pdt),
            sd_dom_pdt = sd(dom_pdt),
            iqr_dom_pdt = IQR(dom_pdt),
            min_dom_pdt = min(dom_pdt),
            max_dom_pdt = max(dom_pdt)) %>% mutate(
            ci_test =  Rmisc::group.CI(dom_pdt ~ gruppe, data = aov_pdt, ci = .95))

mean_dom_pdt_gruppe 

mean_dom_pdt_condition <-  aov_pdt %>% dplyr::group_by(condition) %>%
    dplyr::summarise(mean_pdt = mean(dom_pdt),
            median_dom_pdt = median(dom_pdt),
            sd_dom_pdt = sd(dom_pdt),
            iqr_dom_pdt = IQR(dom_pdt),
            min_dom_pdt = min(dom_pdt),
            max_dom_pdt = max(dom_pdt)) %>% dplyr::mutate(
            ci_test =  Rmisc::group.CI(dom_pdt ~ condition, data = aov_pdt, ci = .95))

mean_dom_pdt_condition 

ci_gc =  Rmisc::group.CI(dom_pdt ~ condition * gruppe, data = aov_pdt, ci = .95)

mean_dom_pdt_condition_gruppe <- aov_pdt %>% dplyr::group_by(gruppe, condition) %>%
    dplyr::summarise(mean_pdt = mean(dom_pdt),
            median_dom_pdt = median(dom_pdt),
            sd_dom_pdt = sd(dom_pdt),
            iqr_dom_pdt = IQR(dom_pdt),
            min_dom_pdt = min(dom_pdt),
            max_dom_pdt = max(dom_pdt)) %>% dplyr::left_join(ci_gc, by = c("gruppe","condition"))

mean_dom_pdt_condition_gruppe           
```

Testing assumptions
```{r}

bp_dom_pdt <- ggpubr::ggboxplot(aov_pdt, x = "gruppe", y = "dom_pdt", color = "condition", palette = "jco" , add = c("mean_se"))
bp_dom_pdt

outliers_dom_pdt <- aov_pdt %>%
  dplyr::group_by(gruppe, condition) %>%
  rstatix::identify_outliers(dom_pdt)
outliers_dom_pdt

shapiro_dom_pdt <- aov_pdt %>%
  dplyr::group_by(gruppe, condition) %>%
  rstatix::shapiro_test(dom_pdt)
shapiro_dom_pdt

levene_dom_pdt <- aov_pdt %>%
  dplyr::group_by(condition) %>%
  rstatix::levene_test(dom_pdt ~ gruppe)
levene_dom_pdt 

dom_pdt_naf <- aov_pdt %>% rstatix::drop_na(dom_pdt)
box_dom_pdt<- rstatix::box_m(dom_pdt_naf[,"dom_pdt", drop = FALSE], dom_pdt_naf$gruppe)
box_dom_pdt

#no extreme outliers
#HC-View not normally distributed
#CP-(Baseline,Imagine,View) not normally distributed
#No homogeneity of variances for Imagine and VR
#No homogeneity of covariances

```

Calculating mixed anova and robust mixed anova
```{r}
anovapdt <- rstatix::anova_test(data=aov_pdt, dv= dom_pdt, wid = id, between =gruppe,
                       within= condition,effect.size = "pes")

rstatix::get_anova_table(anovapdt, correction = "auto")

WRS2::bwtrim(dom_pdt ~ gruppe * condition, id = id, data = aov_pdt)
```

Get CIs for PES
```{r}
e_pdt <- stats::aov(dom_pdt ~ condition * gruppe + Error(id/condition), data = aov_pdt)
effectsize::eta_squared(e_pdt,alternative = "two.sided", partial = TRUE)
```

Post-Hoc-Tests
Paired-t-Tests Grouped by "gruppe"
```{r}
aov_pdt %>% dplyr::group_by(gruppe) %>%
        rstatix::pairwise_t_test(
         dom_pdt ~ condition, paired = TRUE, pool.sd = FALSE,
         p.adjust.method = "none")

```

Paired-t-tests grouped by "condition" 
```{r}

aov_pdt %>% dplyr::group_by(condition) %>%
        rstatix::pairwise_t_test(
         dom_pdt ~ gruppe, paired = FALSE, pool.sd = FALSE,
         p.adjust.method = "none")
```

Paired-wilcox-Tests Grouped by "gruppe"
```{r}

aov_pdt %>% dplyr::group_by(gruppe) %>% rstatix::pairwise_wilcox_test(dom_pdt ~ condition, paired = TRUE, 
         p.adjust.method = "none")
# No differences between wilcox-test and t-test
```

Paired-wilcox-tests grouped by "condition" 
```{r}

aov_pdt %>% dplyr::group_by(condition) %>% rstatix::pairwise_wilcox_test(dom_pdt ~ gruppe, paired = FALSE, 
         p.adjust.method = "none")
# No differences between wilcox-test and t-test
```


################################# PTT ##############################################################################

Prepare data for ptt analysis
```{r}
aov_ptt <- plyr::arrange(long_d, id)
aov_ptt <- aov_ptt %>% dplyr::mutate(dom_ptt = t01_ptt) %>%
                       droplevels()

aov_ptt <- aov_ptt %>% dplyr::select(id,gruppe,condition,dom_ptt)
```

Get descriptive statistics grouped by group and condition
```{r}
mean_dom_ptt_gruppe <- aov_ptt %>%
  dplyr::group_by(gruppe) %>%
  dplyr::summarise(mean_ptt = mean(dom_ptt),
            median_dom_ptt = median(dom_ptt),
            sd_dom_ptt = sd(dom_ptt),
            iqr_dom_ptt = IQR(dom_ptt),
            min_dom_ptt = min(dom_ptt),
            max_dom_ptt = max(dom_ptt)) %>% mutate(
            ci_test =  Rmisc::group.CI(dom_ptt ~ gruppe, data = aov_ptt, ci = .95))

mean_dom_ptt_condition <-  aov_ptt %>% dplyr::group_by(condition) %>%
    dplyr::summarise(mean_ptt = mean(dom_ptt),
            median_dom_ptt = median(dom_ptt),
            sd_dom_ptt = sd(dom_ptt),
            iqr_dom_ptt = IQR(dom_ptt),
            min_dom_ptt = min(dom_ptt),
            max_dom_ptt = max(dom_ptt)) %>% dplyr::mutate(
            ci_test =  Rmisc::group.CI(dom_ptt ~ condition, data = aov_ptt, ci = .95))


ci_gc =  Rmisc::group.CI(dom_ptt ~ condition * gruppe, data = aov_ptt, ci = .95)

mean_dom_ptt_condition_gruppe <- aov_ptt %>% dplyr::group_by(gruppe, condition) %>%
    dplyr::summarise(mean_ptt = mean(dom_ptt),
            median_dom_ptt = median(dom_ptt),
            sd_dom_ptt = sd(dom_ptt),
            iqr_dom_ptt = IQR(dom_ptt),
            min_dom_ptt = min(dom_ptt),
            max_dom_ptt = max(dom_ptt)) %>% dplyr::left_join(ci_gc, by = c("gruppe","condition"))
           
```

Testing assumptions
```{r}
bp_dom_ptt <- ggpubr::ggboxplot(aov_ptt, x = "gruppe", y = "dom_ptt", color = "condition", palette = "jco" , add = c("mean_se"))
bp_dom_ptt


outliers_dom_ptt <- aov_ptt %>%
  dplyr::group_by(gruppe, condition) %>%
  rstatix::identify_outliers(dom_ptt)
outliers_dom_ptt

shapiro_dom_ptt <- aov_ptt %>%
  dplyr::group_by(gruppe, condition) %>%
  rstatix::shapiro_test(dom_ptt)
shapiro_dom_ptt

levene_dom_ptt <- aov_ptt %>%
  dplyr::group_by(condition) %>%
  rstatix::levene_test(dom_ptt ~ gruppe)
levene_dom_ptt 

dom_ptt_naf <- aov_ptt %>% 
          rstatix::drop_na(dom_ptt)

box_dom_ptt<- rstatix::box_m(dom_ptt_naf[,"dom_ptt", drop = FALSE], dom_ptt_naf$gruppe)
box_dom_ptt

#No outliers
#HC data are not normal distributed
#Homogeneity of Variances
#Homogeneity of Covariances
```

Calculating mixed anova and robust mixed anova
```{r}
anovaptt <- rstatix::anova_test(data=aov_ptt, dv= dom_ptt, wid = id, between =gruppe,
                       within= condition, effect.size = "pes")

rstatix::get_anova_table(anovaptt, correction = "auto")

WRS2::bwtrim(dom_ptt ~ gruppe * condition, id = id, data = aov_ptt)
```

Get CIs for PES
```{r}
e_ptt <- stats::aov(dom_ptt ~ condition * gruppe + Error(id/condition), data = aov_ptt)
effectsize::eta_squared(e_ptt,alternative = "two.sided", partial = TRUE)
```
Post-Hoc-Tests

Paired-t-test
```{r}
aov_ptt %>%
        rstatix::pairwise_t_test(
         dom_ptt ~ condition, paired = TRUE, pool.sd = FALSE,
         p.adjust.method = "none")

```

Paired-Wilcox-Test
```{r}
aov_ptt %>%
        rstatix::pairwise_wilcox_test(
         dom_ptt ~ condition, paired = TRUE, pool.sd = FALSE,
         p.adjust.method = "none")
# no differences between wilcox-test and t-test
```



Prepare PDT and PTT data for p-adjustments
PDT
```{r}
g_pdt <- aov_pdt %>% dplyr::group_by(gruppe) %>%
        rstatix::pairwise_t_test(
         dom_pdt ~ condition, paired = TRUE, pool.sd = FALSE,
         p.adjust.method = "none")
g_pdt <- g_pdt %>% dplyr::mutate(n = 1:length(g_pdt$group1)) %>% dplyr::rename(gruppe_condition = gruppe)
```

```{r}
c_pdt <- aov_pdt %>% dplyr::group_by(condition) %>%
        rstatix::pairwise_t_test(
         dom_pdt ~ gruppe, paired = FALSE, pool.sd = FALSE,
         p.adjust.method = "none")
c_pdt <- c_pdt %>% mutate(n = 1:length(c_pdt$group1)) %>% dplyr::rename(gruppe_condition = condition)
```

```{r}
dom_pdt_mht <- dplyr::bind_rows(g_pdt,c_pdt)
#saveRDS(dom_pdt_mht, "dom_pdt_mht.rds")
```

PTT
```{r}
g_ptt <- aov_ptt %>% dplyr::group_by(gruppe) %>%
        rstatix::pairwise_t_test(
         dom_ptt ~ condition, paired = TRUE, pool.sd = FALSE,
         p.adjust.method = "none")
g_ptt <- g_ptt %>% dplyr::mutate(n = 1:length(g_ptt$group1)) %>% dplyr::rename(gruppe_condition = gruppe)
```

```{r}
c_ptt <- aov_ptt %>% dplyr::group_by(condition) %>%
        rstatix::pairwise_t_test(
         dom_ptt ~ gruppe, paired = FALSE, pool.sd = FALSE,
         p.adjust.method = "none")
c_ptt <- c_ptt %>% dplyr::mutate(n = 1:length(c_ptt$group1)) %>% dplyr::rename(gruppe_condition = condition)
```

```{r}
dom_ptt_mht <- bind_rows(g_ptt,c_ptt)
#saveRDS(dom_ptt_mht, "dom_ptt_mht.rds")
```



