


```{r include=FALSE}
  library(car)
  library(dplyr)
  library(MOTE)
```

Load post-hoc-test data from the different analysis
```{r}
dom_pdt_mht <- readRDS("dom_pdt_mht.rds")
dom_ptt_mht <- readRDS("dom_ptt_mht_neu.rds")
cpm_pdt_mht <- readRDS("cpm_pdt_mht.rds")
cpm_ptt_mht <- readRDS("cpm_ptt_mht_neu.rds")
spat_pdt_mht <- readRDS("spat_pdt_mht.rds")
```

Bind everything to one df
```{r}
all <- dplyr::bind_rows(dom_pdt_mht,dom_ptt_mht,cpm_pdt_mht,cpm_ptt_mht,spat_pdt_mht )
```

Adjust p values
```{r}
all$p.adj <- stats::p.adjust(all$p, method = "BH")
```

Recode so that we end up with following columns:
p.sig = is original p value significant?
p.adj.signif = is adjusted p value significant?
p.adj = adjusted p values
p = oroginal p value
```{r}
all <- all %>% mutate(p.sig = p.adj.signif) %>% mutate(p.adj.signif = p.adj)
all$p.adj.signif <- car::recode(all$p.adj.signif, "0:0.001 = '***'; 0.001000001:0.01 = '**'; 0.010000001:0.05 = '*';
                                  0.050000001:1 = 'ns'")  

all
```


Get only significant results + give the test an id from 1:23
```{r}
all_d <- all %>% dplyr::filter(p.adj.signif != "ns") %>% dplyr::mutate(n_sig = 1:23)
```

Get df with only paired t-tests
```{r}
all_paired <- all_d %>% dplyr::filter(gruppe_condition == "HC" | gruppe_condition == "CP" | gruppe_condition == "spat_pdt_neu" | 	
gruppe_condition == "cpm_dif_ptt" | gruppe_condition == "dom_ptt") %>% mutate(n_paired = 1:17)
```

get df with only independent t-tests
```{r}
all_normal <- all_d %>% dplyr::filter(gruppe_condition != "HC" & gruppe_condition != "CP" & gruppe_condition != "spat_pdt_neu" & gruppe_condition != "dom_ptt" & gruppe_condition != "cpm_dif_ptt") %>% mutate(n_normal = 18:23)
```

Create a df for every significant paired t-test containing ES,CI
1
```{r}
t1 <-  as.matrix(all_paired[1,7])
n1 <-  as.matrix(all_paired[1,5])
es1 <- MOTE::d.dep.t.diff.t(t1, n1, a = 0.05)

df1 <- data.frame(d = es1$d[1,1],
                  low = es1$dlow[1,1],
                  high = es1$dhigh[1,1],
                  stat = es1$t[1,1],
                  n_paired = 1,
                  n = es1$n[1,1])

df1
```

2
```{r}
t2 <-  as.matrix(all_paired[2,7])
n2 <-  as.matrix(all_paired[2,5])
es2 <- MOTE::d.dep.t.diff.t(t2, n2, a = 0.05)
df2 <- data.frame(d = es2$d[1,1],
                  low = es2$dlow[1,1],
                  high = es2$dhigh[1,1],
                  stat = es2$t[1,1],
                  n_paired = 2,
                  n = es2$n[1,1])
```

3
```{r}
t3 <-  as.matrix(all_paired[3,7])
n3 <-  as.matrix(all_paired[3,5])
es3 <- MOTE::d.dep.t.diff.t(t3, n3, a = 0.05)
df3 <- data.frame(d = es3$d[1,1],
                  low = es3$dlow[1,1],
                  high = es3$dhigh[1,1],
                  stat = es3$t[1,1],
                  n_paired = 3,
                  n = es3$n[1,1])
```


4
```{r}
t4 <-  as.matrix(all_paired[4,7])
n4 <-  as.matrix(all_paired[4,5])
es4 <- MOTE::d.dep.t.diff.t(t4, n4, a = 0.05)
df4 <- data.frame(d = es4$d[1,1],
                  low = es4$dlow[1,1],
                  high = es4$dhigh[1,1],
                  stat = es4$t[1,1],
                  n_paired = 4,
                  n = es4$n[1,1])
```


5
```{r}
t5 <-  as.matrix(all_paired[5,7])
n5 <-  as.matrix(all_paired[5,5])
es5 <- MOTE::d.dep.t.diff.t(t5, n5, a = 0.05)
df5 <- data.frame(d = es5$d[1,1],
                  low = es5$dlow[1,1],
                  high = es5$dhigh[1,1],
                  stat = es5$t[1,1],
                  n_paired = 5,
                  n = es5$n[1,1])
```


6
```{r}
t6 <-  as.matrix(all_paired[6,7])
n6 <-  as.matrix(all_paired[6,5])
es6 <- MOTE::d.dep.t.diff.t(t6, n6, a = 0.05)
df6 <- data.frame(d = es6$d[1,1],
                  low = es6$dlow[1,1],
                  high = es6$dhigh[1,1],
                  stat = es6$t[1,1],
                  n_paired = 6,
                  n = es6$n[1,1])
```

7
```{r}
t7 <-  as.matrix(all_paired[7,7])
n7 <-  as.matrix(all_paired[7,5])
es7 <- MOTE::d.dep.t.diff.t(t7, n7, a = 0.05)
df7 <- data.frame(d = es7$d[1,1],
                  low = es7$dlow[1,1],
                  high = es7$dhigh[1,1],
                  stat = es7$t[1,1],
                  n_paired = 7,
                  n = es7$n[1,1])
```

8
```{r}
t8 <-  as.matrix(all_paired[8,7])
n8 <-  as.matrix(all_paired[8,5])
es8 <- MOTE::d.dep.t.diff.t(t8, n8, a = 0.05)
df8 <- data.frame(d = es8$d[1,1],
                  low = es8$dlow[1,1],
                  high = es8$dhigh[1,1],
                  stat = es8$t[1,1],
                  n_paired = 8,
                  n = es8$n[1,1])
```

9
```{r}
t9 <-  as.matrix(all_paired[9,7])
n9 <-  as.matrix(all_paired[9,5])
es9 <- MOTE::d.dep.t.diff.t(t9, n9, a = 0.05)
df9 <- data.frame(d = es9$d[1,1],
                  low = es9$dlow[1,1],
                  high = es9$dhigh[1,1],
                  stat = es9$t[1,1],
                  n_paired = 9,
                  n = es9$n[1,1])
```

10

```{r}
t10 <-  as.matrix(all_paired[10,7])
n10 <-  as.matrix(all_paired[10,5])
es10 <- MOTE::d.dep.t.diff.t(t10, n10, a = 0.05)
df10 <- data.frame(d = es10$d[1,1],
                  low = es10$dlow[1,1],
                  high = es10$dhigh[1,1],
                  stat = es10$t[1,1],
                  n_paired = 10,
                  n = es10$n[1,1])
```

11
```{r}
t11 <-  as.matrix(all_paired[11,7])
n11 <-  as.matrix(all_paired[11,5])
es11 <- MOTE::d.dep.t.diff.t(t11, n11, a = 0.05)
df11 <- data.frame(d = es11$d[1,1],
                  low = es11$dlow[1,1],
                  high = es11$dhigh[1,1],
                  stat = es11$t[1,1],
                  n_paired = 11,
                  n = es11$n[1,1])
```

12
```{r}
t12 <-  as.matrix(all_paired[12,7])
n12 <-  as.matrix(all_paired[12,5])
es12 <- MOTE::d.dep.t.diff.t(t12, n12, a = 0.05)
df12 <- data.frame(d = es12$d[1,1],
                  low = es12$dlow[1,1],
                  high = es12$dhigh[1,1],
                  stat = es12$t[1,1],
                  n_paired = 12,
                  n = es12$n[1,1])
```


13
```{r}
t13 <-  as.matrix(all_paired[13,7])
n13 <-  as.matrix(all_paired[13,5])
es13 <- MOTE::d.dep.t.diff.t(t13, n13, a = 0.05)
df13 <- data.frame(d = es13$d[1,1],
                  low = es13$dlow[1,1],
                  high = es13$dhigh[1,1],
                  stat = es13$t[1,1],
                  n_paired = 13,
                  n = es13$n[1,1])
```


14
```{r}
t14 <-  as.matrix(all_paired[14,7])
n14 <-  as.matrix(all_paired[14,5])
es14 <- MOTE::d.dep.t.diff.t(t14, n14, a = 0.05)
df14 <- data.frame(d = es14$d[1,1],
                  low = es14$dlow[1,1],
                  high = es14$dhigh[1,1],
                  stat = es14$t[1,1],
                  n_paired = 14,
                  n = es14$n[1,1])
```

15
```{r}
t15 <-  as.matrix(all_paired[15,7])
n15 <-  as.matrix(all_paired[15,5])
es15 <- MOTE::d.dep.t.diff.t(t15, n15, a = 0.05)
df15 <- data.frame(d = es15$d[1,1],
                  low = es15$dlow[1,1],
                  high = es15$dhigh[1,1],
                  stat = es15$t[1,1],
                  n_paired = 15,
                  n = es15$n[1,1])
```

16
```{r}
t16 <-  as.matrix(all_paired[16,7])
n16 <-  as.matrix(all_paired[16,5])
es16 <- MOTE::d.dep.t.diff.t(t16, n16, a = 0.05)
df16 <- data.frame(d = es16$d[1,1],
                  low = es16$dlow[1,1],
                  high = es16$dhigh[1,1],
                  stat = es16$t[1,1],
                  n_paired = 16,
                  n = es16$n[1,1])
```

17
```{r}
t17 <-  as.matrix(all_paired[17,7])
n17 <-  as.matrix(all_paired[17,5])
es17 <- MOTE::d.dep.t.diff.t(t17, n17, a = 0.05)
df17 <- data.frame(d = es17$d[1,1],
                  low = es17$dlow[1,1],
                  high = es17$dhigh[1,1],
                  stat = es17$t[1,1],
                  n_paired = 17,
                  n = es17$n[1,1])
```


Bind pairedt t-test stats together
```{r}
paired_stats <- rbind(df1,df2,df3,df4,df5,df6,df7,df8,df9,
               df10,df11,df12,df13,df14,df15,df16,df17)
```

Add p values etc.
```{r}
all_paired2 <- merge(all_paired,paired_stats,by="n_paired")
```


Do the same for independent t-tests

18    1
```{r}
t18 <-  as.matrix(all_normal[1,7])
n18 <-  as.matrix(all_normal[1,5])
n1818 <- as.matrix(all_normal[1,6])
es18 <- MOTE::d.ind.t.t(t18, n18, n1818, a = 0.05)




df18 <- data.frame(d = es18$d[1,1],
                  low = es18$dlow[1,1],
                  high = es18$dhigh[1,1],
                  stat = es18$t[1,1],
                  n_normal = 18,
                  n1a = es18$n1[1,1],
                  n2a = es18$n2[1,1])
```

19    2
```{r}
t19 <-  as.matrix(all_normal[2,7])
n19 <-  as.matrix(all_normal[2,5])
n1919 <- as.matrix(all_normal[2,6])
es19 <- MOTE::d.ind.t.t(t19, n19, n1919, a = 0.05)




df19 <- data.frame(d = es19$d[1,1],
                  low = es19$dlow[1,1],
                  high = es19$dhigh[1,1],
                  stat = es19$t[1,1],
                  n_normal = 19,
                  n1a = es19$n1[1,1],
                  n2a = es19$n2[1,1])
```



20    3
```{r}
t20 <-  as.matrix(all_normal[3,7])
n20 <-  as.matrix(all_normal[3,5])
n2020 <- as.matrix(all_normal[3,6])
es20 <- MOTE::d.ind.t.t(t20, n20, n2020, a = 0.05)




df20 <- data.frame(d = es20$d[1,1],
                  low = es20$dlow[1,1],
                  high = es20$dhigh[1,1],
                  stat = es20$t[1,1],
                  n_normal = 20,
                  n1a = es20$n1[1,1],
                  n2a = es20$n2[1,1])
```


21    4
```{r}
t21 <-  as.matrix(all_normal[4,7])
n21 <-  as.matrix(all_normal[4,5])
n2121 <- as.matrix(all_normal[4,6])
es21 <- MOTE::d.ind.t.t(t21, n21, n2121, a = 0.05)




df21 <- data.frame(d = es21$d[1,1],
                  low = es21$dlow[1,1],
                  high = es21$dhigh[1,1],
                  stat = es21$t[1,1],
                  n_normal = 21,
                  n1a = es21$n1[1,1],
                  n2a = es21$n2[1,1])
```




22    5
```{r}
t22 <-  as.matrix(all_normal[5,7])
n22 <-  as.matrix(all_normal[5,5])
n2222 <- as.matrix(all_normal[5,6])
es22 <- MOTE::d.ind.t.t(t22, n22, n2222, a = 0.05)




df22 <- data.frame(d = es22$d[1,1],
                  low = es22$dlow[1,1],
                  high = es22$dhigh[1,1],
                  stat = es22$t[1,1],
                  n_normal = 22,
                  n1a = es22$n1[1,1],
                  n2a = es22$n2[1,1])
```



23    6
```{r}
t23 <-  as.matrix(all_normal[6,7])
n23 <-  as.matrix(all_normal[6,5])
n2323 <- as.matrix(all_normal[6,6])
es23 <- MOTE::d.ind.t.t(t23, n23, n2323, a = 0.05)




df23 <- data.frame(d = es23$d[1,1],
                  low = es23$dlow[1,1],
                  high = es23$dhigh[1,1],
                  stat = es23$t[1,1],
                  n_normal = 23,
                  n1a = es23$n1[1,1],
                  n2a = es23$n2[1,1])
```



```{r}
normal_stats <- rbind(df18,df19,df20,df21,df22,df23)
```


```{r}
all_normal2 <- merge(all_normal,normal_stats, by = "n_normal")
all_normal2
```


Select only important columns
```{r}
paired_final <- all_paired2 %>% dplyr::select(2:12,14,16:18)
paired_final

normal_final <- all_normal2 %>% dplyr::select(2:12,14,16:18)
normal_final
```
